Kindly Bent to Free Us

### 2019-02-20 kindly/infer/infer.tex
Inference rules for regions.

\begin{lemma}
  Without loss of generality, we can consider that
  kind inequalities in satisfiable constraints
  are only done on kind variables.

  \begin{proof}
    Consider the constraint $\Cleq{k}{k'}\Cand C$.
    \begin{itemize}
    \item If $k$ and $k'$ are both constants, it can be removed.
    \item If the constraint is $\Cleq{\kvar}{\kaff}$ or $\Cleq{\kun}{\kvar}$, it can be removed.
    \item If the constraint is $\Cleq{\kvar}{\kun}$ or $\Cleq{\kaff}{\kvar}$, we
      can substitute $\kvar$ by its value in $C$.
    \end{itemize}
  \end{proof}
\end{lemma}

>>>>

% \begin{lemma}
%   Without loss of generality, we can consider that
%   kind inequalities in satisfiable constraints
%   are only done on kind variables.

%   \begin{proof}
%     Consider the constraint $\Cleq{k}{k'}\Cand C$.
%     \begin{itemize}
%     \item If $k$ and $k'$ are both constants, it can be removed.
%     \item If the constraint is $\Cleq{\kvar}{\kaff}$ or $\Cleq{\kun}{\kvar}$, it can be removed.
%     \item If the constraint is $\Cleq{\kvar}{\kun}$ or $\Cleq{\kaff}{\kvar}$, we
%       can substitute $\kvar$ by its value in $C$.
%     \end{itemize}
%   \end{proof}
% \end{lemma}
